From Net-Zero to Net-Negative: Assessing \hydrogen{} and \carbon{} Network Strategies in Europe

### 2023-11-20 report/submissions/journal/paper/paper.tex
follow up

The Hybrid scenario represents the most integrated network strategy, combining both CO2 and H2 networks. While the cost-reduction compared to the \hydrogen-Net scenario is marginal, the allocation of costs reveals a propagation of cost savings in DAC facilities.

@@

While the share of CC share for the combustion of upgraded biogas (100\%) and Gas in CHP (0\%) remains unchanged across all scenarios, the

>>>>

While the cost-reduction in the Hybrid scenario compared to the \hydrogen-Net scenario is marginal, the allocation of costs reveals a propagation of reduced DAC facilities and increased CC at point sources. The Hybrid scenario relies much heavier on investments into the \hydrogen network which outweigh investments in the \carbon{} network by a factor 4.

@@

While the share of CC share for the combustion of upgraded biogas (100\%) and Gas in CHP (0\%) remains unchanged across all scenarios, the introduction of a
